---
title: " A5 Index"
author: "Ryan Leung"
date: "May 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(knitr)
library(leaflet)
source("analysis.R")
```

## Summary Information
[original data source](https://www.gunviolencearchive.org/reports/mass-shooting)

  Within the mass shooting dataset, there are `r number_of_shootings` shootings. The total 
 number killed is `r number_killed`, and the city most impacted by mass shootings is 
 `r most_impacted`. Most impacted is defined as most number of injuries occurred within a  city. The average amount of deaths per mass shooting is `r avg_deaths` deaths, and the most number of injuries for a given shooting is `r max_injured`.


## Summary Table
```{r summary table, echo = FALSE}
kable(four_st_summ, col.names =  c("state", "total_killed", "total_injured"))
```

## Shooting Incident in New Orleans | May 2018  
On `r inc_date`, there was a [shooting](https://www.nola.com/crime/2018/05/last_straw_hours_after_5_shot.html) in `r inc_city`, `r inc_state`. The shooting left `r inc_injured` people injured and `r inc_killed` deaths. From the article,  
it was said that a local resident had been wanting to move away from the neghborhood due to already high crime rate. All the victims were  
sent to the hospital. 

## Interactive Map
This interactive map displays all the mass shootings that occurred in the U.S. based on the mass shootings data set.
```{r interact map, echo = FALSE}
shootings_map
```

- Most of the shootings occur on the eastern part of the U.S.  
- There are little to no reported shootings along the Western and Northwestern part of the U.S.

## State vs Number of Injured Graph
```{r my plot, echo = FALSE}
my_graph
```

- I chose these states because they're in the centers of majority of shootings.  
- California, Florida, and Illinois have +100 injuries caused by shootings. 
- New York and Tennesse have less than 100 injuries caused by shootings.

